Pillar 1 - Sequential Pattern Mining

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
confidence and lift of AR grade

### Support

```{r}

@@

The function `my_apriori()` applies the apriori algorithm on a set of transactions with the parameters that we have chosen.
```{r my_apriori}

my_apriori <- function(data){

@@

The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
```{r clean_AR}

clean_AR <- function(AR){

@@

```{r AR take}
AR_taken <- transactions %>%
  make_AR(
    data_support = d_support_take, 
    type_rule = rate.take
    )

@@

  make_AR(
    data_support = d_support,
    type_rule = rate.fail
    ) %>%

@@

  make_AR(
    data_support = d_support,
    type_rule = rate.low
    ) %>%

@@

```{r AR TPF}
AR_TPF <- transactions_TPF %>%
  make_AR(
    data_support = d_support, 
    type_rule = rate.fail
  ) %>%

@@

  my_apriori(appearance = NULL) %>%
  clean_AR %>%

  # include rhs.support by hand
  separate(
    rhs, 
    into = c("item", "grade_round"), 
    sep = "_",
    remove = FALSE,
    convert = TRUE
    ) %>%
  left_join(
    d_support_grade,
    by = c("item", "grade_round")
    ) %>%
  mutate(
    rhs.support = support.grade
    ) %>%

@@

rm(d_support_grade, transactions_G)
```

>>>>

### Support
```{r}

@@

The function `my_apriori()` applies the apriori algorithm on a set of transactions with the parameters that we have chosen.
```{r my_apriori}
my_apriori <- function(data){

@@

The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
```{r clean_AR}
clean_AR <- function(AR){

@@

```{r AR take}
AR_taken <- transactions %>%
  make_AR(
    data_support = d_support_TNT, 
    type_rule = rate.take
    )

@@

  make_AR(
    data_support = d_support_PF_HL,
    type_rule = rate.fail
    ) %>%

@@

  make_AR(
    data_support = d_support_PF_HL,
    type_rule = rate.low
    ) %>%

@@

```{r AR TPF}
AR_TPF <- transactions_TPF %>%

  make_AR(
    data_support = d_support_PF_HL, 
    type_rule = rate.fail
  ) %>%

@@

  my_apriori %>%
  clean_AR %>%

  # separate rhs and lhs
  separate(
    rhs,
    into = c("rhs_course", "rhs_grade"),
    sep = "_",
    remove = FALSE,
    convert = TRUE
    ) %>%
  separate(
    lhs,
    into = c("lhs_course", "lhs_grade"),
    sep = "_",
    remove = FALSE,
    convert = TRUE
    ) %>%

  # rhs.support
  left_join(
    d_support_G,
    by = c("rhs_course" = "item", "rhs_grade" = "grade_ceil")
    ) %>%
  mutate(
    rhs.support = support.grade
    ) %>%

  # Confidence and lift
    separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%
  group_by(
    lhs, 
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = max(support),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

  # exclude rules with same course on lhs and rhs
  filter(
    lhs_course != rhs_course,
    count >= 10
    ) %>%

  # for each combination of courses (lhs and rhs), keep AR with highest lift (most informative AR)
  group_by(
    lhs_course, 
    rhs_course
    ) %>%
  top_n(
    1,
    lift
    ) %>%

@@

#rm(d_support_grade, transactions_G)
```
